---
title: "PA1_template"
author: "Qiao Xingyu"
date: "23 January 2017"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



This is for assignment 1 of Coursera Reproducible Research
```{r}
library(ggplot2)
```

Read data after extraction
```{r}
data<-read.csv("activity.csv",header=TRUE)
```
sum data using Tapply then plot histogram
```{r}
steps_day<-tapply(data$steps,data$date,FUN=sum)
hist(steps_day, main="Total no. of steps per day",xlab="Total steps")
```
calculate the mean and median of the steps taken
```{r}

mean_steps<-mean(data$steps,na.rm=TRUE)
median_steps<-median(data$steps,na.rm=TRUE)
```

calculate average then plot time series graph
```{r}
average<-aggregate(x=list(steps=data$steps),by=list(interval=data$interval),FUN=mean,na.rm=TRUE)
ggplot(data=average,aes(x=interval,y=steps))+geom_line()+xlab("5min interval")+ylab("avg no. of steps")
```


find number of steps and find Na values
```{r}
average[which.max(average$steps),]

#find and calculate number of NA values
misvalue<-is.na(data$steps)
table(misvalue)
```

create a function that fill values if NA
```{r}
fillvalues<-function(steps,interval){
    filled<-NA
    if(!is.na(steps))
        filled<-c(steps)
    else 
        filled<-(average[average$interval==interval,"steps"])
    return(filled)
}

#execute function
filled.data<-data
filled.data$steps<-mapply(fillvalues,filled.data$steps,filled.data$interval)
```
plot new graph based on filled values and calculate new median&mean
```{r}

steps_total<-tapply(filled.data$steps,filled.data$date,FUN=sum)
qplot(steps_total,binwidth=500,xlab="Total steps taken each day")
new_mean_steps<-mean(steps_total)
new_median_steps<-median(steps_total)
```
seperate weekdays and weekends
```{r}
Whichday<-function(date){
    day<-weekdays(date)
    if(day %in% c("Monday","Tuesday","Wednesday","Thursday","Friday"))
        return("Weekday")
    else if(day %in% c("Saturday","Sunday"))
        return("Weekend")
    else 
        stop("Unknown date")
}

filled.data$date<-as.Date(filled.data$date)
filled.data$day<-sapply(filled.data$date,FUN=Whichday)
    ```
plot graph with weekdays/weekends
```{r}
new_average<-aggregate(steps~interval+day,data=filled.data,mean)
ggplot(new_average,aes(interval,steps))+geom_line()+facet_grid(day~.)+xlab("5 mins interval")+ylab("No. of steps")

```




